---
title: "Lab7 Multiple Linear regression"
author: "Matthew McCafferty"
date: "11/9/2021"
output: html_document
---

```{r setup, include=TRUE, message=FALSE, warning=FALSE, results=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE)

library(tidyverse)
library(kableExtra)
library(stargazer)
library(palmerpenguins)
library(broom)
library(GGally)
library(modelsummary)
```

## Explore Penguins

Use GGally::ggpairs() to creat pairs plot. 

```{r}
ggpairs(penguins)
```
Lets simplify the variables that we include in our gg pairs plot

-species
-bill_length_mm through body_mass_g

```{r}
penguins %>% 
  select(species, bill_length_mm:body_mass_g) %>% 
  ggpairs(aes(color = species))
```

## Mutiple Linear Regression

Understand the relationships between multiple predictor variables and an outcome which is penguins body mass. 

The different variables we are going to try are:

-species
-flipper length
-sex 
-bill depth

### Model 1

Model body mass based only on flipper length and bill depth
Bad idea... There are important variables missing

```{r}
model_1 <- lm(body_mass_g ~ flipper_length_mm + bill_depth_mm, data = penguins)


# Call Model by name to return only coeeficients:
model_1

# More information on coefficients on 
summary(model_1)

```
If everything elese is held constant, we expect that for each 1mm increase in flipper length, penguin body mass is expected to increase by 51.54g on average. 

The R squared value means 76 percent of variance in the penguin body mass (dependent variable) is explained by the model and bill depth 

We think that a model for penguins body mass should contain  variables species, flipper length, and penguin sex. 

```{r}
model_2 <- lm(body_mass_g ~ flipper_length_mm + species + sex, data = penguins)

# lets check out the coeffecients:
model_2

summary(model_2)

# Try interpreting the coefficients for: flipper length, Gentoo, and male
```
On avg we expect a Gentoo penguin is 836.26g larger than an adeile female penguin if everything else remains constant. 

## Visualize this model

```{r}
ggplot(data = penguins, aes(x= flipper_length_mm, y= body_mass_g)) +
  geom_point(aes(color = species))+
  facet_wrap(~ sex)
```

## A couple ways to get & report MLR model outcomes 

Use broom::tidy to get 

```{r}
penguins_model2_coef <- tidy(model_2)

penguins_model2_coef
```

  

```{r}
plot(model_2)

summary(model_2)
```

## Report Model Outputs in summary table 

Model Summary

```{r}
modelsummary(model_2)
```

Use Stargazer: {r, results='asis'}

```{r, results='asis'}
stargazer(model_2, type = "html")
```


